\chapter{Testing}

% ACTUAL TABLE CODE
\setlength{\tabcolsep}{10pt}
\renewcommand{\arraystretch}{1.6}
\begin{longtable}{| p{1.9cm} | p{2.0cm} | >{\centering\arraybackslash}m{0.7cm} | p{2.1cm} | p{2.1cm} | p{1.5cm} | p{0.8cm} | }
\label{<<Label>>}
\caption{Test Cases}
\label{<<Label>>}
\hline
TestCase ID&Objective&Case&Procedure&Expected Results&Actual Results&Pass /Fail\\
\hline
\endfirsthead
\multicolumn{7}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
TestCase ID&Objective&Case&Procedure&Expected Results&Actual Results&Pass /Fail\\
\hline
\endhead
\hline \multicolumn{7}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot
Check Tools		& To check requirements of different tools. & 1. & a) Open Terminal and enter gcc. & GCC should be available.  & Same as Expected  & Pass \\
		&		&   & b) Open terminal and enter lex  & lex should be available   & Same as Expected   &  Pass  \\ 
		&		&   & c) Open terminal and enter yacc & yacc should be available   & Same as Expected   &  Pass  \\ \hline
  
Program Structure & To check nature of program. & 1. & a) Program should be errorless. & Compilation of program should be successful  & Same as Expected  & Pass \\
		&		&   & b) Program should contains POSIX threads. & Program should create new threads using POSIX API.   & Same as Expected   &  Pass  \\ \hline 

Tokenization & To create different tokens as per constraints. & 1. & a) Datatypes & Different tokens should be generated according to datatypes.  & Same as Expected  & Pass \\  
	     & & 2. & a) Function signature should be tokenized. & Fuction name,number of argument and return type should be tokenized  & Same as Expected  & Pass \\
	     & & 3. & b) POSIX thread's signature should be tokenized. & Thread object,Function name which is executed by thread,number of argument and return type should be tokenized  & Same as Expected  & Pass \\	
	     & & 4. & c) Semaphore signature should be tokenized. & Semaphore name,different semaphore signals should be tokenized  & Same as Expected  & Pass \\
     	     & & 5. & d) mutex signature should be tokenized. & Mutex name,different mutex signals should be tokenized  & Same as Expected  & Pass \\ \hline
	
Parsing & Generate different grammer as per tokens. & 1. & a) Grammer for variable datatypes. & Valid grammer should be generated for datatype.  & Same as Expected  & Pass \\  
	     & & 2. & b) Grammer for function signature. & Valid grammer should be generated for functions. & Same as Expected  & Pass \\
	     & & 3. & c) Grammer for POSIX thread's signature. & Valid grammer should be generated for threads. & Same as Expected  & Pass \\	
	     & & 4. & d) Grammer for API of Semaphore. & Valid grammer should be generated for semaphores & Same as Expected  & Pass \\
     	     & & 5. & e) Grammer for Mutex. & Valid grammer should be generated for mutex & Same as Expected  & Pass \\ \hline

Table Generation.& Different table are genereted according grammers. & 1. & a) Table for variable including global and local. & Valid tables should be generated for datatype including local and global.  & Same as Expected  & Pass \\  
	     & & 2. & b) Table for function signature. & Valid table should be generated for functions. & Same as Expected  & Pass \\
	     & & 3. & c) Table for POSIX thread's signature. & Valid table should be generated for threads. & Same as Expected  & Pass \\	
	     & & 4. & d) Table for API of Semaphore. & Valid table should be generated for semaphores & Same as Expected  & Pass \\
     	     & & 5. & e) Table for shared memory (Log Table ) & Valid table should be generated for shared memory & Same as Expected & Pass \\
             & & 6. & f) Table for Mutex. & Valid table should be generated for mutex & Same as Expected  & Pass \\ \hline 

Analysis of critical section.& Critical sections blocks are detected  & 1.& a) Locking and unlocking mechanism. & Check wheter locking and unlocking mechanism is exist for Critical Section.  & Same as Expected  & Pass \\  
	     & & 2. & b) Critical Section detection.& If critical section isn't synchronized then add it. & Same as Expected  & Pass \\ \hline

		
		 

\end{longtable}
% ACTUAL TABLE CODE END
